---
title: "SCISSORS Simulation Study"
subtitle: "Jack Leary, M.S." 
author: "UNC Lineberger Comprehensive Cancer Center - UF Dept. of Biostatistics"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: journal
    highlight: tango
    code_folding: show
    code_download: true 
    toc: true
    toc_dept: 2
    toc_float: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE); set.seed(312)  # lucky seed
```

# Libraries 

First we'll load in the packages we need to tidy & analyze our simulation results. 

```{r, results='hide'}
library(dplyr)      # data manipulation 
library(Seurat)     # scRNA methods & data structures
library(ggplot2)    # plots
library(targets)    # pipeline tools
library(paletteer)  # plot colors 
```

# Data 

Next we'll load in the outputs from out `{targets}` pipeline. 

```{r}
# pancreas reference 
tar_load(clustres_panc_ncell1000_nclust3)
tar_load(clustres_panc_ncell1000_nclust5)
tar_load(clustres_panc_ncell1000_nclust7)
tar_load(clustres_panc_ncell3000_nclust3)
tar_load(clustres_panc_ncell3000_nclust5)
tar_load(clustres_panc_ncell3000_nclust7)
tar_load(clustres_panc_ncell5000_nclust3)
tar_load(clustres_panc_ncell5000_nclust5)
tar_load(clustres_panc_ncell5000_nclust7)
# lung reference
tar_load(clustres_lung_ncell1000_nclust3)
tar_load(clustres_lung_ncell1000_nclust5)
tar_load(clustres_lung_ncell1000_nclust7)
tar_load(clustres_lung_ncell3000_nclust3)
tar_load(clustres_lung_ncell3000_nclust5)
tar_load(clustres_lung_ncell3000_nclust7)
tar_load(clustres_lung_ncell5000_nclust3)
tar_load(clustres_lung_ncell5000_nclust5)
tar_load(clustres_lung_ncell5000_nclust7)
```

We'll coerce everything into one big dataframe. 

```{r}
sim_results <- purrr::map(ls()[grepl("clustres", ls())], 
                          function(x) {
                            df <- eval(as.symbol(x))
                            df <- mutate(df, 
                                         reference = case_when(stringr::str_detect(x, "panc") ~ "Pancreas", TRUE ~ "Lung"), 
                                         dataset = x)
                            return(df)
                          }) %>% 
               purrr::reduce(rbind) %>% 
               mutate(method = factor(method, levels = c("Hierarchical (Ward)", "K-means (Hartigan-Wong)", "SCISSORS", "Louvain (Seurat)")))
```

# Analysis 

First we'll look at the distribution of ARI values achieved by each method over the entire parameter space. We note that this includes parameter values that are less than optimal for some methods, but this is somewhat realistic as it can be very difficult to obtain parameter optimality without ground truth labels for your data. In practice sub-optimal parameters are often chosen due to reliance on software defaults, researcher inexperience, or stochasticity in methods / analysis. 

```{r, fig.width=10}
p0 <- ggplot(sim_results, aes(x = method, y = ari, fill = method)) + 
      facet_wrap(~reference) + 
      geom_violin(draw_quantiles = 0.5, color = "black", size = 1) + 
      labs(fill = "Method", y = "Adjusted Rand Index") + 
      scale_fill_paletteer_d("MetBrewer::Egypt") + 
      theme_bw(base_size = 14)  + 
      theme(axis.text.x = element_text(angle = 45, hjust = 0.9, vjust = 0.9), 
            axis.title.x = element_blank(), 
            panel.grid.major.x = element_blank())
p0
```

# Save Figures

```{r}
fig_save <- function(plot.obj, plot.name = "", dims = c(8, 5)) {
  ggplot2::ggsave(filename = plot.name, 
                  path = "./figures", 
                  plot = plot.obj, 
                  device = "pdf", 
                  width = dims[1], 
                  height = dims[2], 
                  units = "in", 
                  dpi = "retina")
}
```

